SDR enhancement by clouds

### 2024-03-14 article/article.Rmd
Commit 2024-03-14 17:10

total data points `r ST_total$wattGLB.N`
of which CE are `r ST_total$GLB_diff.N_pos`
and `r ST_total$GLB_diff.N_pos`

>>>>

total data points `r ST_total$wattGLB.N`

of which CE are `r ST_total$GLB_diff.N_pos`

and `r ST_extreme_total$GLB_diff.N_pos` are ECE

```{r echo=F, include=T, warning=FALSE, message=FALSE}
ST_total

cat("\n - - - \n")

ST_extreme_total
